---
title: "Central Limit Theorem demo"
subtitle: "Statistical Inference course project"
author: "Ilya Kochergin"
date: "22 nov 2015"
output: pdf_document
---

```{r}

library(ggplot2)
```

##Overview
[//]: # (Overview: In a few (2-3) sentences explain what is going to be reported on.)


Let's demonstrate, that average computed on sample (sample mean) has distribution that tends to be asymptotically normal. Original random variable in this demo is exponentially  distributed.
```{r}
lambda=0.2 # rate parameter 
n=40       # sample size
nosim=1000 # number of samples
```

###Density of exponentially distributed random variable.
Theoretial $Std. deviation \,(\sigma) =Mean\, (\mu) =1/\lambda$=`r 1/lambda`

```{r,echo=FALSE,fig.height=3}
 ggplot()+stat_function(aes(x=c(-1,8)),fun=dexp,args = list(rate=lambda)) +
  # geom_vline(aes(xintersept=5,color="red"))+
   labs(x="x",title="Distribution density of original random variables")
```


##Simulations
[//]: # (Simulations: Include English explanations of the simulations you ran, with the accompanying R code. Your explanations should make clear what the R code accomplishes.)
We generate `nosim=1000` rows of random numbers (samples). Sample size is `n=40`
```{r}
# Random matrix. Each row is a sample (n=40)
rnd_exp_samples<-  matrix(data=rexp(nosim*n,rate=lambda),ncol = n, byrow = T)

```



##Sample Mean versus Theoretical Mean
[//]: # (Sample Mean versus Theoretical Mean: Include figures with titles. In the figures, highlight the means you are comparing. Include text that explains the figures and what is shown on them, and provides appropriate numbers.)

Theoretical mean $\mu=1/\lambda$
Sample mean is a random variable. We have 1000 sample means
```{r}
mu=1/lambda
# vector of sample means
rnd_exp_samples_means <-  apply(X = rnd_exp_samples,1 ,FUN = mean)
# range of sample means
summary(rnd_exp_samples_means)
```
Sample means centered at `r mean(rnd_exp_samples_means)` near theoretial `r mu`

##Sample Variance versus Theoretical Variance
[//]: # (Sample Variance versus Theoretical Variance: Include figures (output from R) with titles. Highlight the variances you are comparing. Include text that explains your understanding of the differences of the variances.)

Theoretical standard deviation is  $\sigma=1/\lambda\,=\,5$
Theoretical variance is  $\sigma=25$
Sample variance is a random variable. We have 1000 sample variance
```{r}
sigma=1/lambda
# vector of sample means
rnd_exp_samples_vars <-  apply(X = rnd_exp_samples,1 ,FUN = var)
# range of sample variances
summary(rnd_exp_samples_vars)
```
Sample variance is centered at `r mean(rnd_exp_samples_vars)` near theoretial `r sigma^2`

##Distribution
[//]: # (Distribution: Via figures and text, explain how one can tell the distribution is approximately normal.)

Histogram of sample means approches to density of Normal distributon with the following parameters:
```{r}
gaussian_mu = mu
gaussian_sigma = sigma/sqrt(n)
```


```{r}

ggplot(data.frame(x=rnd_exp_samples_means),aes(x)) +
  stat_function(fun=dnorm,args=list(mean=gaussian_mu,sd=gaussian_sigma),col="red",size=2)+
  geom_histogram(aes(y=..density..),fill="green",alpha=0.3,col="green",stat_bin=1/30)

```


