---
title: "The Effect of Vitamin C on Tooth Growth in Guinea Pigs"
subtitle: "Statitistic inference course project"
author: "Ilya Kochergin"
date: "22 nov 2015 "
output: pdf_document
---
## Dataset description from documetation

### Description

The response is the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).

###Format

A data frame with 60 observations on 3 variables.

[,1]	len	numeric	Tooth length
[,2]	supp	factor	Supplement type (VC or OJ).
[,3]	dose	numeric	Dose in milligrams.


[//]: # (Load the ToothGrowth data and perform some basic exploratory data analyses )
```{r}
library(datasets)
data(ToothGrowth)
```

```{r}
library(ggplot2)
ggplot(ToothGrowth, aes(x=factor(dose), y=len, fill=factor(dose)))+geom_boxplot()+facet_grid(.~supp)+labs(title="Toothgrowth depending dose and supplement type")
```

## A basic summary of the data.

```{r}
oj_df=(subset(ToothGrowth,supp=='OJ')[c(1,3)]) # Orange Juice
sd(oj_df$len)
mean(oj_df$len)
vc_df=(subset(ToothGrowth,supp=='VC')[c(1,3)]) # Vitamin C

sd(vc_df$len)
mean(vc_df$len)
```

Standard deviance too diffrent in 2 groups (OJ and VC) so we should 
use parameter var.equal=FALSE in t.test()

## Group dataset by dose 
```{r}
D05  <-  subset(ToothGrowth,dose==.5)
D1  <-  subset(ToothGrowth,dose==1)
D2  <-  subset(ToothGrowth,dose==2)
# number observation in each group:
table(ToothGrowth$supp,ToothGrowth$dose)
```


## T-test of each group

```{r}
T05 <- t.test(len~supp,paired=FALSE,var.equal=FALSE,data=D05)
T1 <- t.test(len~supp,paired=FALSE,var.equal=FALSE,data=D1)
T2 <- t.test(len~supp,paired=FALSE,var.equal=FALSE,data=D2)
```


```{r}
T05$conf.int
T1$conf.int
T2$conf.int

```



## Conclusion
For dose 2 mg the supplement form doesn't have significance
But for doses 0.5 and 1 mg OJ significally better.